Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-08-29 pool_model.tex
formatting
Do separate files for subplots

\begin{abstract}
    \textbf{Notes from Christian}
    Different empirical and inactivation models applied in the estimation
    of parameters and modelling of phenomena in food microbiology, gen-
    eralized Lotka Voltera approach used to describe the interaction of mi-
    croorganisms, mechanistic models utilized to provide more insight into
    the underlying dynamic can all be unified as variations of a new model
    known as three pool model. Compared against the aforementioned
    methods which are applicable in specific applications with some limi-
    tations, the present model turns out to be less complex with general
    applicability, low number of parameters and preferably to explain the
    mechanism of the phenomenon of interest. To illustrate the generality
    of the model, three different examples are reported.
\end{abstract}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift.pdf}

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_2pools_toxin.pdf}

@@

    \includegraphics[width=\columnwidth]{Figures/pool_model_1pool_inhib.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop.pdf}

>>>>

\begin{abstract}\noindent
    \textbf{Notes from Christian}
    Different empirical and inactivation models applied in the estimation
    of parameters and modelling of phenomena in food microbiology, gen-
    eralized Lotka Voltera approach used to describe the interaction of mi-
    croorganisms, mechanistic models utilized to provide more insight into
    the underlying dynamic can all be unified as variations of a new model
    known as three pool model. Compared against the aforementioned
    methods which are applicable in specific applications with some limi-
    tations, the present model turns out to be less complex with general
    applicability, low number of parameters and preferably to explain the
    mechanism of the phenomenon of interest. To illustrate the generality
    of the model, three different examples are reported.
\end{abstract}

@@

    %\includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift2.pdf}

@@

    %\includegraphics[width=\columnwidth]{Figures/pool_model_2pools_toxin.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2pools_toxin1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2pools_toxin2.pdf}

@@

    %\includegraphics[width=\columnwidth]{Figures/pool_model_1pool_inhib.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib2.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib3.pdf}

@@

    %\includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop1.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop2.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop3.pdf}
